Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-11-13 manuscript/manuscript.tex
fix spelling and edit wording of abstract

\begin{abstract}
    Social determinants of health (SDOH) are the conditions in which people are born, 
    grow, live, work, and age, which significantly influence their overall health and 
    well-being. These determinants include factors such as socioeconomic status, education, 
    access to healthcare, and the physical environment. Understanding the interactions of 
    these elements will be essential for addressing health disparities and developing more 
    effective public health policies and interventions.  
\end{abstract}

>>>>

\begin{abstract}
  Social determinants of health (SDoH) are the conditions in which people are born, 
  grow, live, work, and age, significantly influencing their overall health and well-being. 
  These determinants include socioeconomic status, education, access to healthcare, and the 
  physical environment. Understanding the interactions of these elements will be essential for 
  addressing health disparities and developing more effective public health policies and interventions.
\end{abstract}
